Carbon Nucleosynthesis

### 2023-04-01 thesis/tex/main.tex
thesis work

\usepackage{amsmath}	% Advanced maths commands
\usepackage{txfonts}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    citecolor=blue,
    pdftitle={Thesis},
    pdfpagemode=FullScreen,
}
% \usepackage{amssymb}	% Extra maths symbols

@@

\usepackage{natbib}
\usepackage[nottoc,numbib]{tocbibind}
\usepackage[titles]{tocloft} % fig titles
\renewcommand{\cftfigpresnum}{\figurename\enspace}
\setlength{\cftfignumwidth}{5em}
\renewcommand{\cfttabpresnum}{\tablename\enspace}
\setlength{\cfttabnumwidth}{5em}

@@

@@

\chapter{The Equilibrium Approximation}\label{sec:equilibrium}
If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio. Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.  
We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
\begin{equation}
M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
\end{equation}

% y_c^cc = (0.0148 +- 0.00016) Z^{0.154 +- 0.0053}
\begin{equation}
    y_C = (0.004 \pm 0.00002) + (0.008 \pm 0.0001) \text{[M/H]} 
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Data Availability}
\addcontentsline{toc}{chapter}{Data Availability}

The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS. Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article. The statement may refer to original data generated in the course of the study or to third-party data analysed in the article. The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.

>>>>

\usepackage{amsmath}	% Advanced maths commands
\usepackage{txfonts}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
    citecolor=black,
    pdftitle={Thesis},
    pdfpagemode=FullScreen,
}
\urlstyle{same}
% \usepackage{amssymb}	% Extra maths symbols

@@

\usepackage{natbib}
\usepackage[nottoc,numbib]{tocbibind}
% \usepackage[titles]{tocloft} % fig titles
% \renewcommand{\cftfigpresnum}{\figurename\enspace}
% \setlength{\cftfignumwidth}{5em}
% \renewcommand{\cfttabpresnum}{\tablename\enspace}
% \setlength{\cfttabnumwidth}{5em}

@@

\chapter{The Equilibrium Approximation}\label{sec:equilibrium}

Chemical abundances reach an equilibrium. New elements produced in stars balance the elements lost to galactic winds and inside stellar reminants. At the present day, our galaxy has evolved long enough to be well approximated by the chemical equilibriums.

In equilibrium, if we know the yields, than the largest uncertainty is the rate of outflows. This determines the final abundances of evolutionary ... \cite{WAF17}.

If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio. Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.  
We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
\begin{equation}
M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
\end{equation}

% y_c^cc = (0.0148 +- 0.00016) Z^{0.154 +- 0.0053}
\begin{equation}
    y_C = (0.0029 \pm 0.0005) + (0.001 \pm 0.0004) \left(\frac{Z}{Z_\odot}\right)
\end{equation}

With uncertainties 

@@

@@
